MAP566 - Homework assignment #1

### 2024-02-13 homework_clean.Rmd
added: draft work on MM section

```{r,warning=FALSE}
library(readr)
library(dplyr)
library(tidyverse)

@@

@@

>>>>

```{r,warning=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(MASS)

@@

    ```{r}
    sp500_data <- read_csv("sp500_history.csv")
    rmarkdown::paged_table(sp500_data)
    ```

    ```{r}
    sp500_data$DailyReturn <- sp500_data$Close - sp500_data$Open
    rmarkdown::paged_table(sp500_data)
    ```

@@

    ```{r}
    ggplot(sp500_data, aes(x = Date, y = DailyReturn)) +
      geom_histogram(stat = "identity", fill = "skyblue", color = "black", bins = 15) +
      labs(title = "Daily Return of S&P 500 (2007-2010)",
           x = "Date",
           y = "Daily Return") +
      theme_minimal() +
      theme(axis.text.x = element_blank(),
            axis.title.x = element_blank())
    ```

    ```{r}
    fit <- fitdistr(sp500_data$DailyReturn, "normal")

    # Print the fitted parameters
    print(fit)

    # Plot the histogram of daily returns with the fitted Gaussian distribution
    hist(sp500_data$DailyReturn, breaks = 30, freq = FALSE, 
         main = "Histogram of Daily Returns with Fitted Gaussian Distribution",
         xlab = "Daily Return")
    curve(dnorm(x, mean = fit$estimate[1], sd = fit$estimate[2]), 
          col = "blue", lwd = 2, add = TRUE, yaxt = "n")
    ```
